Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-02 Dissertation/Thesis/tex/frontmatter.tex
added & edited sec. 7.2 (NRL flight tests), added patrol split screen @ 2 min

\phdgrad{August 31, 2018}
\defensedate{July 11, 2018}
% Year of completion for copyright page and perhaps other places
\year=2018

@@

First and foremost, I would like to thank my parents. In my younger years, I was not always a great student, but they believed in me. When I struggled, they helped every time. I figured that this is what all parents do, but later I realized how lucky I was. Looking back, my academic career not ending prematurely is largely thanks to my mother and father. They have loved me and supported my academic pursuits, and I am extremely grateful.

I would also like to thank all other parts of my family, including my fianc\'ee, brother, grandparents, aunts, uncles, and cousins. We make it a priority to come together and support each other, even when our careers differ greatly and our lives change unpredictably. Despite the long academic road, and they provide support and love.

@@

 I think that following a passion is something truly special. Even though I find great satisfaction in doing anything well, regardless of how simple or complicated the task, I find myself extremely fortunate to pursue endeavors that I actually find exciting and stimulating. With tremendous support around me, I begin a career in an amazing field and ready to take on future challenges.
}

>>>>

\phdgrad{July 13, 2018}
\defensedate{July 13, 2018}
% Year of completion for copyright page and perhaps other places
\year=2018

@@

First and foremost, I would like to thank my parents. When I was younger, I was not always a great student, but my parents believed in me. When I struggled, they helped every time. I figured that this is what all parents do, but later I realized how lucky I was. Looking back, my academic career not ending prematurely is largely thanks to my mother and father. They have loved me and supported my academic pursuits, and I am extremely grateful.

I would also like to thank all other parts of my family, including my fianc\'ee, brother, grandparents, aunts, uncles, cousins, and close friends. We make it a priority to come together and support each other, even when our careers differ greatly and our lives change unpredictably. Despite the long academic road, they provided consistent support and love.

@@

 I think that finding and pursuing a passion is something truly special. Even though I find great satisfaction in doing anything well, regardless of how simple or complicated the task, I find myself extremely fortunate to pursue endeavors that I actually find exciting and stimulating. With tremendous support around me, I begin a career in an amazing field and ready to take on future challenges.
}

### 2018-07-02 Dissertation/Thesis/tex/results.tex

\subsection{3D Exploration Setup and Paramaters}
The software follows the same structure as in Section \ref{sec:MarsSimulation}, except the Gazebo simulated environment is replaces with experimental equipment. This equipment is identical to the prior experimental example (Section \ref{sec:QuadrotorNRL}), except the experiment took place at the Flight Dynamics and Control Lab (FDCL) inside the second floor of SEH. This environment is smaller with only $6$ cameras, where the x-direction (positive east) spans $-2.0$ m to $2.0$ m, the y-direction (positive north) spans $-2.0$ m to $2.0$ m, and the z-direction (positive vertically up) spans $-0.15$ m to $1.5$ m.

>>>>

\subsection{3D Exploration Setup and Parameters}
The software follows the same structure as in Section \ref{sec:MarsSimulation}, except the Gazebo simulated environment is replaces with experimental equipment. This equipment is identical to the prior experimental example (Section \ref{sec:QuadrotorNRL}), except the experiment took place at the Flight Dynamics and Control Lab (FDCL) inside the second floor of SEH. This environment is smaller with only $6$ cameras, where the x-direction (positive east) spans $-2.0$ m to $2.0$ m, the y-direction (positive north) spans $-2.0$ m to $2.0$ m, and the z-direction (positive vertically up) spans $-0.15$ m to $1.5$ m.
